---
title: "Untitled"
author: "Jo Saul"
date: "14/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(faux)
```

```{r}
#simulate our data
set.seed(123456)
simdf1 <- rnorm_multi(n=100,
            mu=c(50,75),
            sd=c(20,25),
            r=0.7,
            varnames = c('pre', 'post')) %>%
  mutate(group='control')
simdf2 <- rnorm_multi(n=100,
            mu=c(50,88),
            sd=c(20,15),
            r=0.7,
            varnames = c('pre', 'post')) %>%
  mutate(group='intervention')

simdf <- bind_rows(simdf1, simdf2)
simdf.long <- simdf %>% gather(period, score, pre:post)
```

```{r}
#graph
ggplot(simdf.long, aes(x=period, y=score, colour=group)) +
  geom_violin() +
  geom_boxplot() +
  theme_minimal()
```

1. Make boxplots narrower 

2. Max boxplots and centred so they are on top of each violin 

3. Switch pre and post around so they are in chronological order - make sure you don't mess up the x label though!

4. Add actual observations to the plot. NB you will need to dodge them to the same degree! Making them slightly transparent will improve this.

5. Change legend, position and drawn line around it
